---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MohammadLab3

<!-- badges: start -->
<!-- badges: end -->

The goal of MohammadLab3 is to create a tidy data frame of geographical information such as longitude, latitude, order and group from a shape file.

## Installation

You can install the development version of MohammadLab3 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("m-fili/Stat585-Lab3")
```

## Example

This is a basic example which shows you how to use the functions in this package to create a data frame from a shape file.

```{r example}
library(MohammadLab3)
library(ggplot2)
library(dplyr)

# Loading the shape file for Iran
data("Iran")

# Class of the object Iran
'sf' %in% class(Iran)

# Creating the data frame from an sf file
iran_df <- team_2(Iran, tolerance = 0.1)

# Visualize
iran_df %>% 
  ggplot(aes(x = long, y = lat, group = group)) + 
  geom_polygon()
```


